Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-18 papers/clusters.tex
Added some stubs for me to fill in with the discussion

>>>>

ARC: Which known clusters were detected? Which comparably-sized clusters
	were not detected? Why not? (Why not M 15?)

ARC: How do the abundances that we find in these known clusters compare
	with the literature?

ARC: Expand on why these particular abundance projections, with
	comparisons to the literature.

ARC: We should note that the anti-correlations known to exist in GCs
	actually make this a *HARDER* task, since the abundances are
	somewhat arbitrarily structured (rather than normally concentrated)
	in a multi-dimensional space.

ARC: What can be said about the M 53 stars? Since we find GCs which are
	mostly spatially concentrated (e.g., very few sitting elsewhere),
	and then we find M53 "co-cluster" stars all over the halo, does this
	directly speak for evidence of accretion by proto-stellar clusters
	in the high-redshift analogues of the Milky Way?

ARC: In addition to the increased precision, it is very important to
	mention the fact that we report an "abundance" for *everything*.
	Gaps in abundance data from classical spectroscopy are rampant,
	and pose a serious problem even if you want to perform Real World(tm)
	tests of chemical tagging. \thecannon\ has solved this entire
	subset of astronomy.
